Secure Composition \\ of Robust and Optimising Compilers

### 2024-05-27 csf2/main.tex
oob

\paragraph{$\sigma_{\sim^{\Ltms}_{\Lms}}\left(\mssafe\cap\scctsafe\cap\sssafe\right)$}
Consider a trace $\irl{\trace}\in\mssafe$ and remember that $\sim^{\Ltms}_{\Lms}$ is the composition of $\sim^{\Ltms}_{\Ltrg}$ and $\sim^{\Ltrg}_{\Lms}$.
{\em All} traces $\trg{\trace}$ with $\trg{\trace}\sim^{\Ltrg}_{\Lms}\irl{\trace}$ are almost identical to $\irl{\trace}$. 
They differ in memory accesses and crashes, where $\irl{\lightning}$ can be related to a $\trg{\lightning}$ or a memory event, e.g., $\trg{Get\ \loc\ 2}$.
In both cases, the memory access cannot be out of bounds.

>>>>

\paragraph{$\sigma_{\sim^{\Ltms}_{\Lms}}\left(\mssafe\cap\scctsafe\cap\sssafe\right)$}
Consider a trace $\irl{\trace}\in\mssafe$ and remember that $\sim^{\Ltms}_{\Lms}$ is the composition of $\sim^{\Ltms}_{\Ltrg}$ and $\sim^{\Ltrg}_{\Lms}$.
{\em All} traces $\trg{\trace}$ with $\trg{\trace}\sim^{\Ltrg}_{\Lms}\irl{\trace}$ are almost identical to $\irl{\trace}$. 
They differ in memory accesses and crashes, where $\irl{\lightning}$ can be related to a $\trg{\lightning}$ or a memory event, e.g., $\trg{Get\ \loc\ 2}$, for an out-of-bounds access.
In both cases, the memory access cannot be out of bounds.
